---
title: "R Notebook"
output: html_notebook
---
# Library

```{r}
library(R2jags)
```

# Data

```{r}
w <- BDD_a %>% ungroup () %>% pivot_wider(id_cols = Tag_id, names_from = Year, values_from = Weight)
w <- na.omit(w)
w <- w[,-c(1,7)]
w <- as.matrix(w)

jags.data <- list(w = w,
                  f = w[,1],
                  nind = nrow(w), 
                  n.occasions = ncol(w))
```

# First model

L = Linf*(1-exp(-K(t-t0)))
K ~ 1
sd ~ t
Linf ~ 1
t0 ~ 1

## parameters and functions

```{r}

inits = list(list(t0 = runif(1, -3, 1), K = runif(1,0,10), Linf = runif(1,0,300), sd = rep(runif(1,0,300), 6)),
             list(t0 = runif(1, -3, 1), K = runif(1,0,10), Linf = runif(1,0,300), sd = rep(runif(1,0,300), 6)))

parameters = c("t0","K","Linf","sd")

Von_B <- function()
{
  #Priors
  t0 ~ dunif(-3,1)
  K ~ dunif(0,10)
  Linf ~ dunif (0,300)
  for (t in 1:n.occasions){
    sd[t] ~ dunif(0,400)
  }
  #Likelihood
  for (i in 1:nind){
    for (t in 1:n.occasions){
      w[i,t] ~ dnorm(Linf*(1-exp(-K*(t-t0))), 1/(sd[t]^2))
    } # t
  } # i
}
```

## running and resuts

```{r}
results_w <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 3000,
              n.burnin = 1500)

print(results_w, digits = 3)
traceplot(results_w, ask =FALSE)
autocorr.plot(results_w)
```

# model avec la formule de growth plutôt (plus besoin de t0)

L[h+1] = L[h] + dL/dt [h]*t (avec t = 1)
dL/dt = K*(Linf-L)

K ~ 1
sd ~ t
Linf ~ 1
L0 ~ 1

```{r}

inits = list(list(L0 = runif(0, 40, 1), K = runif(1,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)),
             list(L0 = runif(0, 40, 1), K = runif(1,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)))

parameters = c("L0","K","Linf","sd")

Von_B_g <- function()
{
  #Priors
  L0 ~ dnorm(15,1/8)
  K ~ dunif(0,10)
  Linf ~ dunif (0,1000)
  for (t in 1:(n.occasions-1)){
    sd[t] ~ dunif(0,400)}
  #Likelihood
  for (i in 1:nind){
    w[i,1] ~ dnorm(f[i],10000) #dnorm(L0, 1/(sd[1]^2))
    for (t in 2:n.occasions){
      w[i,t] ~ dnorm(w[i,t-1]+K*(Linf-w[i,t-1]), 1/(sd[t-1]^2))
    } # t
  } # i
}
```

## running and resuts

```{r}
results_wg <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B_g,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 3000,
              n.burnin = 1800)

print(results_wg, digits = 3)
traceplot(results_wg, ask =FALSE)
autocorr.plot(results_wg)
```

# model avec la formule de growth plutôt (plus besoin de t0)

L[h+1] = L[h] + dL/dt [h]*t (avec t = 1)
dL/dt = K*(Linf-L)

K ~ t
sd ~ t
Linf ~ 1
L0 ~ 1

```{r}

inits = list(list(L0 = runif(0, 40, 1), K = runif(5,0,10), Linf = runif(1,0,300), sd = rep(runif(1,0,300), 6)),
             list(L0 = runif(0, 40, 1), K = runif(5,0,10), Linf = runif(1,0,300), sd = rep(runif(1,0,300), 6)))

parameters = c("L0","K","Linf","sd")

Von_B_gt <- function()
{
  #Priors
  L0 ~ dnorm(15,1/8)
  #K ~ dunif(0,10)
  Linf ~ dunif (0,1000)
  for (t in 1:n.occasions){
    sd[t] ~ dunif(0,400)}
  for (t in 1:(n.occasions-1)){
    K[t] ~ dunif(0,10)}
  #Likelihood
  for (i in 1:nind){
    w[i,1] ~ dnorm(L0, 1/(sd[1]^2))
    for (t in 2:n.occasions){
      w[i,t] ~ dnorm(w[i,t-1]+K[t-1]*(Linf-w[i,t-1]), 1/(sd[t]^2))
    } # t
  } # i
}
```

## running and resuts

```{r}
results_wgt <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B_gt,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 10000,
              n.burnin = 5000)

print(results_wgt, digits = 3)
traceplot(results_wgt, ask =FALSE)
autocorr.plot(results_wgt)
```

# model avec la formule de growth plutôt (plus besoin de t0)

L[h+1] = L[h] + dL/dt [h]*t (avec t = 1)
dL/dt = K*(Linf-L)

K ~ t
sd ~ 1
Linf ~ 1
L0 ~ 1

```{r}
jags.data <- list(w = w,
                  nind = nrow(w), 
                  n.occasions = ncol(w))

inits = list(list(L0 = runif(0, 40, 1), K = runif(5,0,10), Linf = runif(1,0,300), sd = runif(1,0,300)),#, sd0 =rnorm(1,1/8,0.5)),
             list(L0 = runif(0, 40, 1), K = runif(5,0,10), Linf = runif(1,0,300), sd = runif(1,0,300)))#, sd0 =rnorm(1,1/8,0.5)))

parameters = c("L0","K","Linf","sd")#,"sd0")

Von_B_gt <- function()
{
  #Priors
  L0 ~ dnorm(15,1/8)
  sd ~ dunif(0,400)
  Linf ~ dunif (0,1000)
  #sd0 ~ dnorm(1/8,1)
  for (t in 1:(n.occasions-1)){
    K[t] ~ dunif(0,10)}
  #Likelihood
  for (i in 1:nind){
    w[i,1] ~ dnorm(L0, 1/(sd^2))
    for (t in 2:n.occasions){
      w[i,t] ~ dnorm(w[i,t-1]+K[t-1]*(Linf-w[i,t-1]), 1/(sd^2))
    } # t
  } # i
}
```

## running and resuts

```{r}
results_wgt <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B_gt,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 4000,
              n.burnin = 2000)

print(results_wgt, digits = 3)
traceplot(results_wgt, ask =FALSE)
autocorr.plot(results_wgt)
```

# Model of growth with all consecutive data

# data creation

```{r}
la <- BDD_a %>% group_by(Tag_id, Lake) %>% summarize() %>% ungroup()
mooved <- la[duplicated(la$Tag_id),]$Tag_id
la <- la %>% filter ( !duplicated(la$Tag_id))
la <- la %>% mutate (Lake = ifelse(Tag_id %in% mooved, NA, Lake))
tr <- BDD_a %>% group_by(Tag_id, Treatment) %>% summarize() %>% ungroup()
mooved <- tr[duplicated(tr$Tag_id),]$Tag_id
tr <- tr %>% filter ( !duplicated(tr$Tag_id))
tr <- tr %>% mutate (Treatment = ifelse(Tag_id %in% mooved, NA, Treatment))


t <- BDD_a %>% ungroup () %>% pivot_wider(id_cols = Tag_id, names_from = Year, values_from =Size)
t <- merge(t, tr)
t <- t[,-c(1,8)]
#t <- as.matrix(t)

tbl = data.frame()
for (i in 1:nrow(t)){
  for (j in 1:(ncol(t)-2)){
    if (!is.na(t[i,j]) & !is.na(t[i,j+1])){
      tbl <- rbind(tbl, c(t[i,j], t[i,j+1], t$Treatment[i]))
    }
  }
}

colnames(tbl) <- c("t1","t2","Treatment")

tbl <- tbl[!is.na(Treatment),]

jags.data <- list(y = tbl$t2,
                  nind = nrow(tbl),
                  Treatment = tbl$Treatment,
                  f = tbl$t1)
```

# Inits and functions

```{r}
inits <- function(){
  list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300))
}
#inits = list(list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)))

parameters = c("K","Linf","sd")

growth_vonB <- function()
{
  #Priors
  K ~ dunif(0,10)
  Linf ~ dunif(0,300)
  sd ~ dunif(0,200)
  #Likelihood
  for (i in 1:nind){
    y[i] ~ dnorm(f[i]+K*(Linf-f[i]), 1/(sd^2))
  }
}

growth_result <- jags.parallel(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = growth_vonB,
              n.chains = 3,
              #method = 'parallel',
              n.iter = 1000,
              n.burnin = 500)

print(growth_result, digits = 3)
traceplot(growth_result, ask =FALSE)
autocorr.plot(growth_result)
```

# running and results

```{r}
inits <- function(){
  list(sd = runif(1,0,200), K = runif(4,0,10), Linf = runif(1,0,300))
}
#inits = list(list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)))

parameters = c("K","Linf","sd")

growth_vonB <- function()
{
  #Priors
  for (tr in 1:4){
    K[tr] ~ dunif(0,10)}
  Linf ~ dunif(0,300)
  sd ~ dunif(0,200)
  #Likelihood
  for (i in 1:nind){
    y[i] ~ dnorm(f[i]+K[Treatment[i]]*(Linf-f[i]), 1/(sd^2))
  }
}

growth_result <- jags.parallel(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = growth_vonB,
              n.chains = 3,
              #method = 'parallel',
              n.iter = 1000,
              n.burnin = 500)

print(growth_result, digits = 3)
traceplot(growth_result, ask =FALSE)
autocorr.plot(growth_result)
```

```{r}
inits <- function(){
  list(sd = runif(1,0,200), K = runif(4,0,10), Linf = runif(4,0,300))
}
#inits = list(list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)),
#             list(sd = runif(1,0,200), K = runif(1,0,10), Linf = runif(1,0,300)))

parameters = c("K","Linf","sd")

growth_vonB <- function()
{
  #Priors
  for (tr in 1:4){
    K[tr] ~ dunif(0,10)
    Linf[tr] ~ dunif(0,300)}
  sd ~ dunif(0,200)
  #Likelihood
  for (i in 1:nind){
    y[i] ~ dnorm(f[i]+K[Treatment[i]]*(Linf[Treatment[i]]-f[i]), 1/(sd^2))
  }
}

growth_result <- jags.parallel(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = growth_vonB,
              n.chains = 3,
              #method = 'parallel',
              n.iter = 1000,
              n.burnin = 500)

print(growth_result, digits = 3)
traceplot(growth_result, ask =FALSE)
autocorr.plot(growth_result)
```

# Trying to see the influence of treatment

```{r}
tr <- BDD_a %>% group_by(Tag_id, Treatment) %>% summarize() %>% ungroup()
mooved <- tr[duplicated(tr$Tag_id),]$Tag_id
tr <- tr %>% filter ( !duplicated(tr$Tag_id))
tr <- tr %>% mutate (Treatment = ifelse(Tag_id %in% mooved, NA, Treatment))
```

```{r}
la <- BDD_a %>% group_by(Tag_id, Lake) %>% summarize() %>% ungroup()
mooved <- la[duplicated(la$Tag_id),]$Tag_id
la <- la %>% filter ( !duplicated(la$Tag_id))
la <- la %>% mutate (Lake = ifelse(Tag_id %in% mooved, NA, Lake))
```

```{r}
w <- BDD_a %>% ungroup () %>% pivot_wider(id_cols = Tag_id, names_from = Year, values_from = Weight)
w <- w %>% merge(la) %>% merge(tr)
w <- w[!is.na(w$`2016`)&!is.na(w$`2017`)&!is.na(w$`2018`)&!is.na(w$`2019`)&!is.na(w$`2020`)&!is.na(w$`2021`),]

jags.data <- list(w = w[,c(2:7)],
                  f = w$`2016`,
                  Lake = w$Lake,
                  Treatment = w$Treatment,
                  nind = nrow(w[,c(2:7)]), 
                  n.occasions = ncol(w[,c(2:7)]))
```

```{r}

inits = list(list(L0 = runif(0, 40, 1), K = runif(4,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)),
             list(L0 = runif(0, 40, 1), K = runif(4,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)))

parameters = c("L0","K","Linf","sd")

Von_B_g_cov <- function()
{
  #Priors
  L0 ~ dnorm(15,1/8)
  Linf ~ dunif (0,1000)
  for (t in 1:(n.occasions-1)){
    sd[t] ~ dunif(0,400)}
  for (treatment in 1:4){
    K[treatment] ~ dunif(0,10)}
  #Likelihood
  for (i in 1:nind){
    w[i,1] ~ dnorm(f[i],100000) #dnorm(L0, 1/(sd[1]^2))
    for (t in 2:n.occasions){
      w[i,t] ~ dnorm(w[i,t-1]+K[Treatment[i]]*(Linf-w[i,t-1]), 1/(sd[t-1]^2))
    } # t
  } # i
}
```

```{r}
vonB_cov <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B_g_cov,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 1000,
              n.burnin = 500)

print(vonB_cov, digits = 3)
traceplot(vonB_cov, ask =FALSE)
autocorr.plot(vonB_cov)
```
```{r}
inits = list(list(L0 = runif(0, 40, 1), K = runif(16,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)),
             list(L0 = runif(0, 40, 1), K = runif(16,0,10), Linf = runif(1,0,300), sd = runif(5,0,300)))

parameters = c("L0","K","Linf","sd")

Von_B_g_cov_l <- function()
{
  #Priors
  L0 ~ dnorm(15,1/8)
  Linf ~ dunif (0,1000)
  for (t in 1:(n.occasions-1)){
    sd[t] ~ dunif(0,400)}
  for (lake in 1:16){
    K[lake] ~ dunif(0,10)}
  #Likelihood
  for (i in 1:nind){
    w[i,1] ~ dnorm(f[i],100000) #dnorm(L0, 1/(sd[1]^2))
    for (t in 2:n.occasions){
      w[i,t] ~ dnorm(w[i,t-1]+K[Lake[i]]*(Linf-w[i,t-1]), 1/(sd[t-1]^2))
    } # t
  } # i
}
```

```{r}
vonB_cov_l <- jags(data = jags.data,
              inits = inits,
              parameters.to.save = parameters,
              model.file = Von_B_g_cov_l,
              n.chains = 2,
              #method = 'parallel',
              n.iter = 1000,
              n.burnin = 500)

print(vonB_cov_l, digits = 3)
traceplot(vonB_cov_l, ask =FALSE)
autocorr.plot(vonB_cov_l)
```


```{r}
param <- data.frame(rbind(as.mcmc(vonB_cov)[[1]],as.mcmc(vonB_cov)[[2]]))
```

```{r}
ggplot(param)+
  geom_density(aes(x = K.1.), color = "red")+
  geom_density(aes(x = K.2.), color = "blue")+
  geom_density(aes(x = K.3.), color = "green")+
  geom_density(aes(x = K.4.), color = "black")
```






